Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-09-13 docs/00-manuscripts/mdpi/manuscript.tex
add featurless learner to learner list
update author order

% Authors, for the paper (add full first names)
\Author{Patrick Schratz $^{1}$\orcidA{}*, Jannes Muenchow $^{1}$\orcidB{}, José Cortés $^{1}$\orcidC{}, Eugenia Iturritxa $^{2}$\orcidD{}, Bernd Bischl $^{3}$\orcidE{} and Alexander Brenning $^{1,}$\orcidF{}}

@@

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
	This is an example of a quote.
\end{quote}

@@

\begin{itemize}
	\item  Extreme Gradient Boosting (XGBoost)
	\item  Random Forest (RF)
	\item  Penalized Regression (L1 (lasso) and L2 (ridge))
	\item  Support Vector Machine (SVM, RBF Kernel)
\end{itemize}

RF and SVM are well established algorithms and widely used in (environmental) remote sensing.
Extreme Gradient Boosting (commonly abbreviated as XGBoost) has shown promising results in benchmark studies in recent years.
Penalized regression is a statistical modeling technique capable of dealing with highly-correlated covariates by penalizing the coefficients of the model \cite{hastie2001}.
Common penalties are 'lasso' (L1) and 'ridge' (L2).
Ridge does not remove variables from the model (penalization to zero) but just shrinks them to effectively zero, keeping them in the model.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, Patrick Schratz and Alexander Brenning; methodology, Patrick Schratz, José Cortés, Jannes Muenchow and Bernd Bischl; software, Patrick Schratz; validation, Patrick Schratz and Alexander Brenning; formal analysis, Patrick Schratz, Alexander Brenning, José Cortés and Bernd Bischl; investigation, Patrick Schratz; resources, Eugenia Iturritxa and Patrick Schratz; data curation, Patrick Schratz and Eugenia Iturritxa; writing---original draft preparation, Patrick Schratz; writing---review and editing, Patrick Schratz and Alexander Brenning; visualization, Patrick Schratz; supervision, Alexander Brenning and Bernd Bischl; project administration, Alexander Brenning; funding acquisition, Alexander Brenning. All authors have read and agreed to the published version of the manuscript.}

>>>>

% Authors, for the paper (add full first names)
\Author{Patrick Schratz $^{1}$\orcidA{}*, Jannes Muenchow $^{1}$\orcidB{}, Eugenia Iturritxa $^{2}$\orcidD{}, José Cortés $^{1}$\orcidC{}, Bernd Bischl $^{3}$\orcidE{} and Alexander Brenning $^{1,}$\orcidF{}}

@@

@@

\begin{itemize}
	\item  Extreme Gradient Boosting (XGBoost)
	\item  Random Forest (RF)
	\item  Penalized Regression (L1 (lasso) and L2 (ridge))
	\item  Support Vector Machine (SVM, RBF Kernel)
	\item  Featureless learner
\end{itemize}

RF and SVM are well established algorithms and widely used in (environmental) remote sensing.
Extreme Gradient Boosting (commonly abbreviated as XGBoost) has shown promising results in benchmark studies in recent years.
Penalized regression is a statistical modeling technique capable of dealing with highly-correlated covariates by penalizing the coefficients of the model \cite{hastie2001}.
Common penalties are 'lasso' (L1) and 'ridge' (L2).
Ridge does not remove variables from the model (penalization to zero) but just shrinks them to effectively zero, keeping them in the model.
A featureless learner was included for a baseline comparison.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, Patrick Schratz and Alexander Brenning; Data curation, Patrick Schratz and Eugenia Iturritxa; Formal analysis, Patrick Schratz, José Cortés, Bernd Bischl and Alexander Brenning; Funding acquisition, Alexander Brenning; Investigation, Patrick Schratz; Methodology, Patrick Schratz, Jannes Münchow, José Cortés and Bernd Bischl; Project administration, Alexander Brenning; Resources, Eugenia Iturritxa; Software, Patrick Schratz; Supervision, Bernd Bischl and Alexander Brenning; Validation, Patrick Schratz and Alexander Brenning; Visualization, Patrick Schratz; Writing – original draft, Patrick Schratz; Writing – review \& editing, Jannes Münchow, José Cortés and Alexander Brenning.}
